---
title: "Behnke_Abgabe_2"
author: "Gabriel Valentin Behnke"
date: "24 4 2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Tasks

1. Read in the data contained in this .csv file into R as an R data.frame object in the R workspace.
```{r}
setwd("C:/Users/super/Documents/sdm/Abgabe_2/data")
dataset <- read.csv("dummydata.csv")
```
2. What are the data types of each column?
```{r}
class(dataset$family)
class(dataset$genus)
class(dataset$species)
class(dataset$error)
class(dataset$quality)
class(dataset$comment)
```
3. Save the column entitled “error” as a vector object in the R workspace.
```{r}
error<-dataset$error
is.vector(error)
```
4. Remove all rows with values larger than 1 in the “error” column and save the result as a new R object.
```{r}
index_error<-error<=1
data_neg_1<-dataset[index_error,]
```
5. Write out this cleaned object to your local “output” folder as a new .csv file.
```{r}
write.csv(data_neg_1,"data_neg_1")
data_neg_1
```
