---
title: "Abgabe_3"
author: "Gabriel Valentin Behnke"
date: "4 5 2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Solution
```{r,include=FALSE}
library("raster")
```
Create a map of your country of residence with the following features:

1. a raster background map showing elevation data,
```{r}
elev <- getData("worldclim", var="alt", res=10)
```
2. a vector map showing the country boundary,
```{r}
ger <- getData('GADM', country='DEU', level=0)
```
3. use the vector map to clip the raster map,
```{r}
crop_elev <- crop(elev, extent(ger))
clip_elev <- mask(crop_elev, ger)
plot(clip_elev)
plot(ger, add=T)
```

4. map point locations denoting the places of residence of the course participants in your country (if any), which you can enter here (use a SpatialPointsDataFrame object with the correct CRS for this task),
```{r}
grp <- read.csv("C:/Users/super/Documents/sdm/Abgabe_3/Input/participant_locations.csv")
lola <- grp[,c(3,2)]
spdf <- SpatialPointsDataFrame(coords = lola, data = grp, proj4string = CRS("+proj=longlat +datum=WGS84 +ellps=WGS84 +towgs84=0,0,0"))
plot(clip_elev)
plot(ger, add=T)
plot(spdf, add=T)
```

5. map the three largest cities of your selected country with different symbols, and
```{r}
plot(clip_elev)
plot(ger, add=T)
plot(spdf, add=T)
points(13.404954,52.520008,pch=8,cex=2)
points(9.993682,53.551086,pch=12,cex=2)
points(11.576124,48.137154,pch=14,cex=2)
```

6. get bonus points by adding a legend, rivers, and other cartographic elements as well as
```{r}
plot(clip_elev)
plot(ger, add=T)
plot(spdf, add=T)
points(13.404954,52.520008,pch=8,cex=2)
points(9.993682,53.551086,pch=12,cex=2)
points(11.576124,48.137154,pch=14,cex=2)
legend("bottomright",legend = c("Residences","Berlin","Hamburg","Muenchen"),pch = c(3,8,12,14),title="Places")
```

7. the distances of the places of residence to Marburg.
```{r}
list_a <- cbind(lola[,1],lola[,2])
spDistsN1(list_a,c(8.7667933,50.8021728),longlat = TRUE)
```

